\texttt{bayesim}: a tool for fast model fitting with Bayesian inference

### 2018-08-23 paper/Manuscript.tex
latest paper version

\section*{Model}
  \todo[inline]{Should this section title actually just be ``Technical Background`` as well perhaps?}

@@

\section*{Application Examples}
  \subsection{Ideal Diode Model}
    \begin{itemize}
      \item validation example - ``observed'' data is just generated using the model and we show we can recover the correct input parameters
      \item figure 3 showing PMF
    \end{itemize}

>>>>

\section*{Technical Background}

@@

\section*{Application Examples}
  \subsection{Ideal Diode Model}
    As a first example, we fit a simple two-parameter model of solar cell current density $J$ (as a function of voltage $V$ and temperature $T$) known as the ideal diode model:

    \begin{equation}
      J(V,T) = J_L+J_0\left(\exp{\frac{qV}{nkT}}-1\right)
    \end{equation}

    where $k=8.61733\times 10^{-5}$ eV/K is Boltzmann's constant, by convention $J_L$ (the light current) is negative and $J_0$ (the saturation current) is positive but strongly dependent on temperature, a dependence we can approximate as:

    \begin{equation}
      J_0 \approx B'T^{3/n}\exp{\left(\frac{-E_{g0}}{nkT}\right)}
    \end{equation}

    where $E_{g0}$ is the zero-temperature bandgap of the material. For this example, we will set this to 1.2 eV and $J_L$ to -0.03 mA/cm$^2$. There are thus two parameters to be fit, the coefficient $B'$ (which can range over a wide variety of values) and the ideality factor $n$ (which is by definition between 1 and 2).

    As validation, we generate the ``observations" using the same model we'll use for fitting, with parameter values of $n=1.36$ and $B'=258$, and four temperature values of 150, 200, 250, and 300 K.
